%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[calibri]{../macdowell-cv/mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{E. Daniel Blancas Reyes}
\address{Mexico City \linebreak Mexico}
\contacts{edblancas.github.io \linebreak edblancas@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer}{AMK Technologies}{Jun 2017 -- Sep 2018}
			API for Exposing Internal Services
			\begin{itemize}
				\item Lead engineer, in charge of a team of 3 developers. Built from the ground an API to expose the internal services to subscribe users to an entertainment newsletter via cellphone carriers.
			\end{itemize}
			Frontend for the Back Office
			\begin{itemize}
				\item Creation of the base project, built with React/Redux, for the back office services.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{Indigo}{Sep 2016 -- Jun 2017}		
			Mexican Goverment Bank
			\begin{itemize}
				\item Lead frontend engineer, reviewing the code base and implementing in the team: good practices, clean code, and code refactoring. Using AngularJS.
				\item Processing big quantity of information to produce reports, implemented by using Spring Batch and Jasper Reports.
			\end{itemize}
			Flights and Hotel Reservations Agency
			\begin{itemize}
				\item The project was staled for almost half a year, so they gave it to me to finish some service integrations and server architecture. The project was built in Ruby and Rails, and I was the only developer.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{Glider Software Solutions}{May 2012 -- Sep 2016}	
			\begin{itemize}
				\item Support role in the redesign of a core project that orchestrated the aperture of new bank accounts, using design patterns, TDD, and best code practices.
				\item Migration of the frontend of the account aperture system, from FELX to HTML (JS/jQuery).
				\item Lead engineer in the building of a frontend for a new financial client, it consumed REST Services and exposed small services consumed internally. I presented a demo with Grails, and JS/jQuery, that ultimately were accepted and built upon those technologies.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Intern}{Yum! Restaurants International}{Jun 2008 -- Jan 2009}
			Financial Reports			
			\begin{itemize}
				\item Reduced the missing toys between the provider and each franchise branch office by implementing a project that polled the quantity received from the provider, and sending a weekly email to the financial department with a report.
				\item Implemented a custom survey for the financial department to post recommendations of new reports.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Mexico City}{Tec de Monterrey}{2005 -- 2012}
			\begin{itemize}
				\item Engineering in Computer Technologies, May 2010. CENEVAL National Prize (EGEL Test).
				\item Master's Degree in Computer Science, May 2012. Full scholarship with monthly maintenance fee by CONACYT and Tec de Monterrey.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Intelligent Tutor System for the Training of Novice Operators of a Combined Cycle Power Plant} (2012). Web based classroom where the professors designs exercises for training operators, it has a 3D model of the power plant, use freesteam open source library for the vapor tables, and grade the operators with the help of Bayesian Networks (Elvira tool). Java, C, MySQL.
				\item \textbf{Timbrao} (2017). Project that helps Mexican people to automatize their tax declarations by taking a photo to their receipts from some stores.  PHP, JavaScript, Angular 2+, iOS.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Programming languages:} Java; JavaScript; Ruby (Prior Experience); C (Prior Experience); SQL.
				\item \textbf{Tools and technologies:} Maven; Dropwizard; HBase; Kafka; JUnit; Mockito; Ruby on Rails; React/Redux; AngularJS; Angular 2+; Git; Bash; Docker; NGINX; MySQL; TDD; Design Patterns; Clean Code; IntelliJ IDEA; DataGrip; VIM; Visual Studio Code.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
