%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[calibri]{../macdowell-cv/mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% For links
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{colortbl}
% http://latexcolor.com/
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\definecolor{nocolor}{rgb}{1.0, 1.0, 1.0}
% url colors
\hypersetup{colorlinks=true, linkcolor=cobalt, urlcolor=cobalt}
% table color
\arrayrulecolor{nocolor}

% Set applicant's personal data for header
\name{E. Daniel Blancas Reyes}
\address{Mexico City \linebreak Mexico}
\contacts{\href{https://edblancas.io}{edblancas.io} \linebreak \href{mailto:edblancas@gmail.com}{edblancas@gmail.com}}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Senior Software Engineer}{Nubank}{May 2021 -- Present}
			\begin{itemize}
				\item Built a solution in the fraud vertical that helped to decrease in 15\% the time spent by customer service to process customers that could be identified as potential fraudsters. Technologies used: Clojure, ClojureScript, Kafka, Datomic, and K8s.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Full Stack Engineer}{Rappi}{Jul 2019 -- May 2021}
			\begin{itemize}
				\item Coaching a small team to migrate the old microservices to a new event-based architecture mainly with Kotlin (Spring Boot) and Kafka, but we also used TypeScrpit (NestJS); that resulted in a more robust infrastructure that powers the Colombian's RappiPay B2B ecosystem. Other technologies used: PostgreSQL, Jenkins, and K8s.
				\item Built a solution, with Airflow and Python3, that helped in the day-to-day settlement transactions processed by RappiPay systems with Rappi's debit card. This led to an automated process and a more precise and rapid resolution to tens of thousands of support tickets for Mexico and Brasil. Other technologies used: Pandas, Snowflake, K8s.
				\item Developed new features in the RappiPay vertical, which helped to stabilize the functioning of the platform and make more attractive the use of Rappi's debit card. Technologies used: Node.js, JavaScript with Express/Koa, PostgreSQL, and K8s.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{AMK Technologies}{Jun 2017 -- Sep 2018}
			\begin{itemize}
				\item Led the design and development of a high demand API for registering users to entertainment subscriptions, this helped the company attract new clients. So clients could do their own advertisement of new products and subscribe users using the API. Technologies used: Spring (Core, JDBC), Dropwizard, HBase, Kafka, MySQL, MongoDB, Java 11, Maven, TDD, AngularJS, Angular 2+, React/Redux, and Docker.
				\item Standardized creation of the frontend projects (React and Redux).
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{Indigo}{Sep 2016 -- Jun 2017}		
			\begin{itemize}
				\item Supervised the frontend code base (AngularJS) for Bansefi back office, implementing and teaching best practices, clean code, and incremental refactoring.
				\item Solved the need of process big CSV files of inventory for Bansefi, by implementing a batch process (Spring Batch) and printing PDF reports with Jasper Reports.
				\item Led the redesign and development of a ``Flights and Hotel Reservation'' Ruby on Rails project, that was staled for almost half a year, because there was no Ruby developer. So I had to organize meetings with the previous developer, and then do weekly meetings with the client to report advance and clarify doubts. Culminating in successful end to end tests that implied third party API's.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Mexico City}{Tec de Monterrey}{2005 -- 2012}
			\begin{itemize}
				\item \textbf{M.S Computer Science}, Apr 2012. Full scholarship with monthly maintenance fee by CONACYT and Tec de Monterrey.
				\item \textbf{B.S Computer Engineering}, May 2010. CENEVAL National Prize, Egress Test (EGEL).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Other Projects}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Intelligent Tutor System for the Training of Novice Operators of a Combined Cycle Power Plant} (2012). Web based classroom where the professors designs exercises for training operators, it has a 3D model of the power plant, use freesteam open source library for the vapor tables, and grade the operators with the help of Bayesian Networks (Elvira tool). Java, C, MySQL.
				\item \textbf{Timbrao} (2017). Project that helps Mexican people to automatize their tax declarations by taking a photo to their receipts from some stores.  PHP, JavaScript, Angular 2+, iOS.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Engilsh (Professional working proficiency); Spanish (Native).
				\item Clojure; ClojureScript; Java; Kotlin; JavaScript; TypeScript; Python; SQL; NoSQL.
				\item REPL Driven Development; Scrum; Agile; Microservices; CI/CD; Event-Based Architecture; TDD; Unit Tests; Integration Tests; E2E Tests.
				\item Datomic; Pedestal; Leiningen; Node.js; Express; Koa; NestJS; Pandas; Airflow; Maven/Gradle; Dropwizard; Spring; HBase; Kafka; React/Redux; AngularJS; Angular 2+; Git; Docker; Jenkins; Tekton; AWS (IAM, ECS, S3); K8s.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{flushleft}
		CV with introduction, gap between jobs, prior experience, and other projects available at: \linebreak \url{https://edblancas.io/cv/cv.pdf}
	\end{flushleft}
	
\end{document}
